\title{\mtitle}
\author{\mauthor}
\date\today

\maketitle

\begin{itemize}
\item Github repository containing programs and results:
\end{itemize}
\begingroup
\begin{center}
	\url{https://github.com/evenmn/Urban-Sound-Classification}
\end{center}
\endgroup
\vspace{1.5cm}

\begin{abstract}
The aim of this project is to divide various sounds into ten categories, inspired by the \href{https://datahack.analyticsvidhya.com/contest/practice-problem-urban-sound-classification/}{Urban Sound Challenge}. For that we have investigated the performance of logistic regression and various neural networks, like Feed-forward Neural Networks (FNNs), Convolutional Neural Networks (CNNs) and Recurrent Neural Networks (RNNs). 

When it comes to error estimation, accuracy score is a natural choice. Various activation functions were examined, and regularization was added for the logistic case. As optimization tool ADAM was mainly used, with a various number of epochs and different batch sizes. 
	
To extract features from our dataset (dimensionality reduction), we used a spectrogram in the CNN case, and Mel Frequency Ceptral Coefficients (MFCCs) for FNN and RNN. We also tried two different RNNs, namely the Long Short-Term Memory (LSTM) network and the Gated Recurrent Unit (GRU) network. 

All the neural networks were more or less able to recognize the training set, but it was a significantly difference in validation accuracy. FNN provided the highest validation accuracy of 94\%, followed by LSTM (88\%), GRU (86\%) and CNN (82\%). Our linear model, logistic regression, was able to classify just 60\% of the validation set correctly. 
\end{abstract}

\newpage
\tableofcontents

%\newpage

